%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsthm}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nyx Haile} \\ \vspace{1pt}
    \small  \href{mailto:xyn@mit.edu}{\underline{xyn@mit.edu}} $|$ 
    \href{https://www.linkedin.com/in/nyx-haile-bb6711228}{\underline{LinkedIn}} $|$
    \href{https://github.com/nyx-haile}{\underline{GitHub}}
\end{center}

\newcommand*{\cls}[3]{%
    \href{https://student.mit.edu/catalog/m#1#3.html\##1.#2}{\underline{#1.#2}}}%
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Massachusetts Institute of Technology}{Cambridge, MA}
      {B.S., Computer Science, B.S., Mathematics, Minor in Economics}{Exp. Grad. May 2026}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Mentor}{September 2023 -- Present}
      {The SHED}{Cambridge, MA}
      \resumeItemListStart
        \resumeItem{Served as a key mentor in a cutting-edge, interdisciplinary makerspace, guiding research projects at the intersection of biocomputing, human-computer interaction (HCI), and personal transportation.}
        \resumeItem{Provided comprehensive technical training to laboratory staff on advanced equipment, ensuring compliance with safety protocols and optimizing experimental outcomes.}
        \resumeItem{Spearheaded the design and execution of innovative research methodologies, employing data-driven decision-making to solve challenges in increasing makerspace access}
        \resumeItem{Collaborated with interdisciplinary teams to advance research in computational models, machine learning applications, and data analytics, supporting the integration of quantitative techniques in experimental workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Researcher}{June 2025 -- Present}
      {Weiss Laboratory for Synthetic Biology}{Cambridge, MA}
      \resumeItemListStart
        \resumeItem{Applied theoretical computer science techniques—including graph algorithms, spatial optimisation, and formal constraint modelling—to develop a generative design pipeline for biologically constrained microarchitectures.}
        \resumeItem{Integrated AI-based prompting with classical algorithmic tools to synthesise spatially feasible geometries under physical and physiological constraints, enabling rapid and adaptable iteration.}
        \resumeItem{Designed custom validation metrics and refinement algorithms grounded in discrete geometry and computational topology to ensure manufacturability and biological viability.}
        \resumeItem{Bridged computational design with experimental workflows by contributing to high-throughput analysis pipelines, including sequencing, imaging, and real-time control system interfacing.}
        \resumeItem{Designed and managed high-performance computing infrastructure to support LLM-assisted vascular mesh generation, including workstation configuration, benchmarking, and cross-platform STL validation for experimental export.}
      \resumeItemListEnd
    
    \resumeSubheading
        {AI Developer}{December 2022 -- July 2023}{Vana}{Remote}
        \resumeItemListStart
            \resumeItem{Organized the Vana X MIT Generative AI Hackathon, managing a \$25,000 prize pool and coordinating logistics, outreach, and judging criteria, resulting in the participation of top-tier talent from the MIT community.}
            \resumeItem{Designed, developed, and rigorously tested a robust framework for hackathon participants, leveraging JavaScript and Python to create an efficient and scalable platform for generative AI development.}
            \resumeItem{Created a messaging applet in Swift utilizing the Vana API, integrating user-friendly functionalities while ensuring seamless interaction between backend and frontend components.}
            \resumeItemListEnd


    
    
    % \resumeSubheading
    %   {Tech Lead}{December 2021 -- April 2022}
    %   {Bluehour}{Cambridge, MA}
    %   \resumeItemListStart
    %     \resumeItem{Pioneered the design and development of core frameworks in designing and building the core frameworks for the Bluehour system, working directly with the founder to create scalable, decentralized solutions from the ground up.}
    %     \resumeItem{Authored smart contracts in Solidity to manage complex token burn/mint mechanics, enhancing system efficiency and contributing to Bluehour's overall token economy.}
    %     \resumeItem{Conducted in-depth analysis of user feedback from test runs, using data-driven insights to pivot development strategies, optimizing the platform for a more intuitive and engaging consumer-facing experience.}
    %     \resumeItem{Took on broad responsibilities, from design decisions to technical implementation, demonstrating versatility in a startup environment with a focus on rapid iteration and quantitative feedback loops.}
        
    % \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      % \resumeProjectHeading
      %     {\textbf{Howtowin.lol} $|$ \emph{Python, Redis, Svelte, OLAP DB}}{July 2024-- Present}
      %     \resumeItemListStart
      %       \resumeItem{Developing a vector matching algorithm to identify and compare gameplay metrics with similar past matches.}
      %       \resumeItem{Building a website in Svelte to display data and manage user logins,}
      %       \resumeItem{Designing data visualization tools to present insights and recommendations to users effectively}
      %     \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Howtowin.lol} $|$ \emph{Python, Redis, Svelte, OLAP DB}}{July 2024-- Present}
          \resumeItemListStart
            \resumeItem{Developing a vector matching algorithm to identify and compare gameplay metrics with similar past matches.}
            \resumeItem{Building a website in Svelte to display data and manage user logins,}
            \resumeItem{Designing data visualization tools to present insights and recommendations to users effectively}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.1625in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, C/C++/C\#, SQL (Postgres), Redis, HTML/CSS, } \\
     \textbf{Frameworks}{: React, Node.js, Svelte, Flask} \\
     \textbf{Developer Tools}{: Git, *NIX, Docker, Google Cloud Platform} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, TensorFlow}
    }}\\
    \textbf{Tools}{: Fusion360, Adobe Suite, Arduino, Xcode }
 \end{itemize}
\section{Relevant Coursework}
    \cls{6}{5660}{a}, \cls{6}{5620}{a}, \cls{6}{5630}{a}, \cls{18}{032}{a}, \cls{6}{1010}{a}, \cls{18}{650}{b}, \cls{6}{1210}{a}, \cls{18}{06}{a},  \cls{6}{1200}{a}, \cls{18}{404}{a}, \cls{14}{01}{a},
    [Descriptions Linked]
    

%-------------------------------------------
\end{document}
